Data Exploration: IUCN and AquaMaps

### 2015-12-02 data_explore_2015_data.Rmd
script uses new data

# Data files
#iucn spp cells WITHOUT extinct locations of IUCN subpopulations
iucn_spp_cells <- read_csv(file.path(dir_anx, 'explore_am_v_iucn/iucn_spp_cells_both_2015.csv'), 
                           col_types = 'cdddd', progress = TRUE) %>%
  as.data.frame() %>%
  filter(presence != 5) ### removes extinct subpopulations

@@

if(!file.exists(data_file)) {
  ### species info list - scinames, IUCN species ID, AM species ID, category etc
  spp_list_base <- read.csv('shiny/data/spp_am_v_iucn_2015.csv', stringsAsFactors = FALSE)

@@

spp_list <- read.csv(data_file, stringsAsFactors = FALSE)
```

@@

spp_list <- spp_list %>%
  mutate(area_ratio = am_area / iucn_area,
         area_ratio = ifelse(area_ratio > 1, 1 / area_ratio, area_ratio),
         area_ratio = area_ratio * 100)

>>>>

# Data files
#iucn spp cells WITHOUT extinct locations of IUCN subpopulations
iucn_spp_cells <- read_csv(file.path(dir_anx, 'explore_am_v_iucn/iucn_spp_cells_2015.csv'), 
                           col_types = 'cdddd', progress = TRUE) %>%
  as.data.frame() %>%
  filter(presence != 5) ### removes extinct subpopulations

@@

if (!file.exists(data_file)) {
  ### species info list - scinames, IUCN species ID, AM species ID, category etc
  spp_list_base <- read.csv('data/spp_am_v_iucn_2015_inclDD.csv', stringsAsFactors = FALSE)

@@

spp_list1 <- read.csv(data_file, stringsAsFactors = FALSE)
```

Note: At this point the species list (`spp_list1`) still contains data deficient species.  274 species show zero area for IUCN; most of these are DD.  The next chunk filters for `!is.na(sm_perc)` and `popn_category != 'DD'`

``` {r eliminate DD and NA areas, echo = FALSE, warning = FALSE}
spp_list <- spp_list1 %>% 
  filter(!is.na(sm_perc))

DT::datatable(spp_list %>%
                 select(sciname, am_sid, iucn_sid, am_review = reviewed, 
                        cat = popn_category, trend = popn_trend, spp_group, 
                        A_tot = total_area, A_am = am_area, A_iucn = iucn_area, 
                        sm_perc, sm_range, area_ratio, lg_area_pct))

@@
